Category-Level Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection

### 2016-10-27 paper/lncsFormat.tex
add the experiment of fastText
changed to lncs format

\def\year{2017}\relax
\documentclass{article}
\usepackage{aaai17}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\frenchspacing
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}

@@

\usepackage{hyperref}
\setcounter{secnumdepth}{2}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Category-Pivot Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection}
%构造（building）一个**词表（找一个词对它更合适的描述），for transfer learning in accurate event detection
%\title{Constructing Knowledge Base's Category Topics for Transfer Learning in Accurate Microblog Event Detection}
\maketitle

@@

The customized knowledge bases such as EVIN\cite{kuzey2014evin}, Event Registry\cite{leban2014eventRegistry}, and Storybase\cite{wu2015storybase}, are designed for managing events.
These knowledge bases are mainly built on news articles.
EVIN maps the existing event-related news articles into semantic classes. 
Event Registry collects the articles by the API of News Feed Service\cite{trampuvs2012newsfeed}, then detects events, and provides the structural information of the events, such as the related Wikipedia article, timestamp, and location etc. 
Storybase introduces Wikipedia current events\footnote{\url{https://en.wikipedia.org/wiki/Portal:Current_events}} as the resources for constructing event-and-storyline knowledge base on news articles, which are provided by GDELT project\cite{leetaru2013gdelt}.
As the news articles may lag behind the microblogs when the emergency of events, it's not enough to detect events from microblog stream by directly applying these customized knowledge bases.

@@

\textbf{Overall Performances.}
\begin{comment}
Table 1 reports the number of events
detected, the precision and recall, of the three methods respectively.
The results of EDCoW are reproduced from [21]9
. Shown in the
table, our proposed method Twevent yields the best precision of
86.1\% which is significantly larger than the precisions achieved
by EDCoW and Tweventu. Observe that our method Twevent detects
101 events with a recall of 75 realistic events. On the same
dataset, EDCoW detects 21 events in total with 13 realistic events.
Tweventu yields a slighter worse precision than EDCoW (75.3%
vs 76.2\%) but detects the largest number of realistic events. In
terms of DERate, Twevent achieves the lowest rate despite that our
method detects much more events than EDCoW (101 vs 21). On
the other hand, we observe that Tweventu delivers the worst DERate,
more than double of Twevent (41\% vs 16.0\%). That is, the unigrams
about the same event are clustered into two or more events.
Because a tweet segment usually conveys very specific information,
the tweets containing the tweet segment are all about the same
topic (e.g., the event). Two tweet segments about the same event
are therefore have higher chance to be clustered together.
\end{comment}

\textbf{Discussions.} 
%An accurate recent states learning leads to accurate event detection.
These methods work in four ways. 
1) Based on topic model, BurstyBTM and TimeUserLDA detect bursty topics. 
Although they are designed for batch learning initially, we run them on the slide windows to adapt to the text stream environment.
2) Integrated with knowledge base, Twevent detects bursty segments, groups them into clusters, and then filters out the meaningless ones by Wikipedia.
3) By clustering articles, UMass System and LSH decide whether the article belongs to the existing event or a new one.
As designed for First Story Detection task (one of the Topic Detection and Tracking subtasks\cite{allan2012topic}) initially, they prefer to enlarge the recall of detected events. 
4) By analyzing word frequencies, EDCoW clusters the bursty words into events.

@@

\newpage
\bibliographystyle{aaai}
\small
\bibliography{paperbib}

>>>>

% !Mode:: "TeX:UTF-8"
\documentclass[runningheads,a4paper]{llncs}

%\usepackage{aaai17}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\frenchspacing
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}

@@

\usepackage{hyperref}
\setcounter{secnumdepth}{2}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Category-Level Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection}
\titlerunning{Transfer Learning for Accurate Event Detection}
%构造（building）一个**词表（找一个词对它更合适的描述），for transfer learning in accurate event detection
%\title{Constructing Knowledge Base's Category Topics for Transfer Learning in Accurate Microblog Event Detection}
\begin{comment}% for double blind
\author{Weijing Huang\inst{1} \and Wei Chen\inst{1} \thanks{Corresponding author.}\and Tengjiao Wang\inst{1}}
\institute{Key Laboratory of High Confidence Software Technologies (Ministry of Education), EECS, Peking University, Beijing, China \\ 
\path{huangwaleking@gmail.com,{pekingchenwei,tjwang}@pku.edu.cn}\\ 
}
\end{comment}

\maketitle

@@

The customized knowledge bases such as EVIN\cite{kuzey2014evin}, Event Registry\cite{leban2014eventRegistry}, and Story-base\cite{wu2015storybase}, are designed for managing events.
These knowledge bases are mainly built on news articles.
EVIN maps the existing event-related news articles into semantic classes. 
Event Registry collects the articles by the API of News Feed Service\cite{trampuvs2012newsfeed}, then detects events, and provides the structural information of the events, such as the related Wikipedia article, timestamp, and location etc. 
Storybase introduces Wikipedia current events\footnote{\url{https://en.wikipedia.org/wiki/Portal:Current_events}} as the resources for constructing event-and-storyline knowledge base on news articles, which are provided by GDELT project\cite{leetaru2013gdelt}.
As the news articles may lag behind the microblogs when the emergency of events, it's not enough to detect events from microblog stream by directly applying these customized knowledge bases.

@@

\textbf{Overall Performances.}
\begin{CJK*}{UTF8}{gbsn}
    中文范例！超级长的一句中文    中文范例！超级长的一句中文    中文范例！超级长的一句中文    中文范例！超级长的一句中文
\end{CJK*}

\begin{comment}
Table 1 reports the number of events
detected, the precision and recall, of the three methods respectively.
The results of EDCoW are reproduced from [21]9
. Shown in the
table, our proposed method Twevent yields the best precision of
86.1\% which is significantly larger than the precisions achieved
by EDCoW and Tweventu. Observe that our method Twevent detects
101 events with a recall of 75 realistic events. On the same
dataset, EDCoW detects 21 events in total with 13 realistic events.
Tweventu yields a slighter worse precision than EDCoW (75.3%
vs 76.2\%) but detects the largest number of realistic events. In
terms of DERate, Twevent achieves the lowest rate despite that our
method detects much more events than EDCoW (101 vs 21). On
the other hand, we observe that Tweventu delivers the worst DERate,
more than double of Twevent (41\% vs 16.0\%). That is, the unigrams
about the same event are clustered into two or more events.
Because a tweet segment usually conveys very specific information,
the tweets containing the tweet segment are all about the same
topic (e.g., the event). Two tweet segments about the same event
are therefore have higher chance to be clustered together.
\end{comment}

\textbf{Discussions.} 
%An accurate recent states learning leads to accurate event detection.
\begin{comment}
These methods work in four ways. 
1) Based on topic model, BurstyBTM and TimeUserLDA detect bursty topics. 
Although they are designed for batch learning initially, we run them on the slide windows to adapt to the text stream environment.
2) Integrated with knowledge base, Twevent detects bursty segments, groups them into clusters, and then filters out the meaningless ones by Wikipedia.
3) By clustering articles, UMass System and LSH decide whether the article belongs to the existing event or a new one.
As designed for First Story Detection task (one of the Topic Detection and Tracking subtasks\cite{allan2012topic}) initially, they prefer to enlarge the recall of detected events. 
4) By analyzing word frequencies, EDCoW clusters the bursty words into events.
\end{comment}

@@

\newpage
\bibliographystyle{unsrt}
\small
\bibliography{paperbib}
